A Quantitative Approach to Book Printing in Sweden and Finland, 1640–1828

### 2018-10-10 inst/examples/201808-HistoricalMethods-Figures.Rmd

```{r Figure_14, echo=FALSE, message=FALSE, warning=FALSE}
# Take cities from SNB except Turku
df00 <- df.full %>% filter(publication_year >= 1640 & publication_year <= 1850)
df1 <- df00 %>% filter((publication_place %in% setdiff(cities, "Turku") & Catalogue == "SNB") |
                       (publication_place %in% "Turku" & Catalogue == "FNB")) 
df1$publication_place[!df1$publication_place == "Stockholm"] <- "Other"
df1$publication_place <- droplevels(as.factor(as.character(df1$publication_place)))

>>>>

```{r Figure_14, echo=FALSE, message=FALSE, warning=FALSE}
# Take cities from SNB except Turku
df00 <- df.full.1911 %>% filter(publication_year >= 1640 & publication_year <= 1850)
df1 <- df00 %>% filter((publication_place %in% setdiff(cities, "Turku") & Catalogue == "SNB") |
                       (publication_place %in% "Turku" & Catalogue == "FNB")) 
df1$publication_place[!df1$publication_place == "Stockholm"] <- "Other"
df1$publication_place <- droplevels(as.factor(as.character(df1$publication_place)))
